\sysfull

### 2018-08-02 paper/asplos19/abstract.tex
changes

@@

Embedded devices in the Internet of Things gain new deployment opportunities when their hardware is free of batteries and powered by ambient energy. Energy harvested from the environment, however, is unpredictable and can only power a device intermittently. In the intermittent execution model, computation is frequently interrupted by power failures, and to make forward progress, the system must save intermediate program state into non-volatile memory. Task-based programming models that execute at the granularity of statically-defined tasks, offer an efficient alternative to checkpointing. Existing task-based systems, however, fix their task size at compile time and operate without any regard to the changing energy conditions at runtime. When tasks are sized without accounting for available energy, state may be persisted either more frequently than necessary or not frequently enough for the program to make progress and terminate. To address these challenges, we propose \sys, an \emph{adaptive} task-based execution model that progresses on a multi-tasks scale, when energy permits (\emph{efficiency}), and preserves the computation progress on a sub-task scale when needed. \sys ensures that power failures cannot leave the program state in non-volatile memory inconsistent using a specialized memory virtualization mechanism. Our evaluation on a real energy-harvesting device demonstrates the benefits of adaptive task coalescing and downscaling, and highlights \sys's performance improvements over a state-of-art task-based system.

>>>>

%

@@

%
% Embedded devices in the Internet of Things gain new deployment opportunities when their hardware is free of batteries and powered by ambient energy. Energy harvested from the environment, however, is unpredictable and can only power a device intermittently. In the intermittent execution model, computation is frequently interrupted by power failures, and to make forward progress, the system must save intermediate program state into non-volatile memory. Task-based programming models that execute at the granularity of statically-defined tasks, offer an efficient alternative to checkpointing. Existing task-based systems, however, fix their task size at compile time and operate without any regard to the changing energy conditions at runtime. When tasks are sized without accounting for available energy, state may be persisted either more frequently than necessary or not frequently enough for the program to make progress and terminate. To address these challenges, we propose \sys, an \emph{adaptive} task-based execution model that progresses on a multi-tasks scale, when energy permits (\emph{efficiency}), and preserves the computation progress on a sub-task scale when needed. \sys ensures that power failures cannot leave the program state in non-volatile memory inconsistent using a specialized memory virtualization mechanism. Our evaluation on a real energy-harvesting device demonstrates the benefits of adaptive task coalescing and downscaling, and highlights \sys's performance improvements over a state-of-art task-based system.
%
Freeing embedded devices from batteries is a key factor in developing the energy neutral Internet of Things. 
Energy harvesting, however, is unpredictable and can only power a device intermittently. Therefore, the two paradigms of intermittent execution (checkpointing and task-based) save intermediate programs states into non-volatile memory frequently, to preserve a program forward progress. Despite the superiority of the task-based approach, however, it fixes their task size at compile time and operates obliviously to the changing energy conditions. When a program divided into tasks for heterogeneous energy buffers it will be persisted either more frequently than necessary or not frequently enough for the program to make progress and terminate. To address these challenges, we propose \sys, an \emph{adaptive} and \emph{efficient} task-based execution model. \sys progresses on a multi-tasks scale, when energy permits and preserves the computation progress on a sub-task scale if necessary. \sys ensures that power failures cannot leave the program state in non-volatile memory inconsistent using a specialized memory virtualization mechanism. Our evaluation shows that \sys is $2X$ faster than the state-of-the-art system in most cases and is able to progress where static systems fail.
